---
title: "CueStrength between subjects"
author: "Manuel Bohn"
date: "17 3 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)


## importing data
d <- bind_rows(read_csv(file="cue.btw.look.data.csv"),
               read_csv(file="cue.btw.lookLabel.data.csv"),
               read_csv(file="cue.btw.point.data.csv"),
               read_csv(file="cue.btw.pointLabel.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

```

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

```

Plot with all data for all conditions. Looks pretty similar to the within result.
```{r plot overall}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = condition, y = mean, fill = condition)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("look", "lookLabel","point","pointLabel"),
                     labels=c("Look", "Look + Label","Point","Point + Label"))
```

Plot for trial 1. This time, point seems to be slightly off
```{r plot trial 1}
ms <- d %>%
  filter(trial == "1") %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = condition, y = mean, fill = condition)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("look", "lookLabel","point","pointLabel"),
                     labels=c("Look", "Look + Label","Point","Point + Label"))
```

Effect of target object location on table. Inner = closer to the agent, outer = further away. 
General bias to pick the inner object, considerably stronger for point. Probably because the poitning finger is closer to the inner object.  
```{r inner vs outer location}
## performance in training and test
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(targetOnTable,condition, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = condition, y = mean, fill = condition,frame = targetOnTable)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~ targetOnTable) +
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) +
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("look", "lookLabel","point","pointLabel"),
                     labels=c("Look", "Look + Label","Point","Point + Label"))

```

Condition by trial overall. Looks pretty random.
```{r plot trials}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition, trial, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = condition)) +
  geom_line(aes(group= condition)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

Conditions by agents.
```{r trials per condition and agent}
# d %>%
#   filter(trial_type == "test") %>%
#   group_by(agent,condition) %>%
#   summarise(n = length(agent), 
#             correct = mean(correct)) %>%
#   knitr::kable(digits = 2)
```

Agent effects, looks all good
```{r plot agents}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition, agent, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = agent, y = mean, col = condition)) +
  geom_line(aes(group= condition)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

Bayesian t-tests comparing to chance.
```{r tests against chance}
## Bayesian t-tests comapring to chance
library(BayesFactor)


d %>%
  filter(trial_type == "test") %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 0.5))$bf) %>%
  select(condition,mean,bf) %>%
  knitr::kable(digits = 3)
 
```

Brm Model, same error message but Rhats look fine. Confirming that condition does not matter, at least for adults.
```{r model}
## model
library(brms)

data_inf <- d %>%
  filter(trial_type == "test")%>%
  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))

# registered  model
bm <- brm(correct ~ condition +
              (1 |id) + (condition |agent), 
          data = data_inf, family = bernoulli(),
          save_all_pars = TRUE,
          control = list(adapt_delta = 0.80),
          iter = 5000)

summary(bm)


```


