---
title: "CueStrength controls (between subject)"
author: "Manuel Bohn"
date: "26 3 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)


## importing data
d <- bind_rows(read_csv(file="cue_control_test.data.csv"),
               read_csv(file="cue_control_barrier.data.csv"),
               read_csv(file="cue_control_later.data.csv"),
               read_csv(file="cue_control_1.data.csv"),
               read_csv(file="cue_control_2.data.csv"),
               read_csv(file="cue_within.data.csv"),
               read_csv(file="cue.btw.look.data.csv"),
               read_csv(file="cue.btw.lookLabel.data.csv"),
               read_csv(file="cue.btw.point.data.csv"),
               read_csv(file="cue.btw.pointLabel.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test")) %>%
  mutate(control = ifelse(is.na(control) , "test", control)) %>%
  mutate(condition = ifelse(control == "no" | control == "test" , condition, control)) %>%
  mutate(phase = ifelse(control == "test", "Cues", "Controls")) %>%
  mutate(design = ifelse(experiment == "cue_strength_controls" | experiment == "cue_strength_controls_replication" | experiment == "cue_strength_within" , "within", "between"))

```

```{r plot overall}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition ,design, id) %>%
  summarise(correct = mean(correct)) 

ms2 <- ms %>%
  multi_boot_standard(col = "correct")


ggplot() +
  geom_jitter(data = ms, aes(x = condition, y = correct, col = condition, alpha = .2), width = .2,height = .015)+
  geom_pointrange(data = ms2,aes(x = condition, y = mean, col = condition,ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_grid( design ~ . , scales = "free_x", space = "free_x" ) +
  theme_few(base_size = 12) + 
  ylim(-0.05,1.05)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  guides(alpha = F)+
  scale_color_solarized(name="Condition",
                     breaks=c("abs", "bar","look", "lookLabel","point", "pointLabel"),
                     labels=c("Control - Later", "Control - Barrier","Test - Look", "Test - Look + Label", "Test - Point", "Test - Point + Label"))

```

```{r plot overall bar}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition ,design, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")  

ggplot(ms, 
       aes(x = condition, y = mean, fill = condition)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_grid( design ~ . , scales = "free_x", space = "free_x" ) +
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("abs", "bar","look", "lookLabel","point", "pointLabel"),
                     labels=c("Control - Later", "Control - Barrier","Test - Look", "Test - Look + Label", "Test - Point", "Test - Point + Label"))
```


```{r plot by phase}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition, phase ,design, id) %>%
  summarise(correct = mean(correct)) 

ms2 <- ms %>%
  multi_boot_standard(col = "correct")


ggplot() +
  geom_jitter(data = ms, aes(x = condition, y = correct, col = condition, alpha = .2), width = .2,height = .015)+
  geom_pointrange(data = ms2,aes(x = condition, y = mean, col = condition,ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .5), size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_grid( design ~ phase , scales = "free_x", space = "free_x" ) +
  theme_few(base_size = 12) + 
  ylim(-0.05,1.05)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  guides(alpha = F)+
  scale_color_solarized(name="Condition",
                     breaks=c("abs", "bar","look", "lookLabel","point", "pointLabel"),
                     labels=c("Control - Later", "Control - Barrier","Test - Look", "Test - Look + Label", "Test - Point", "Test - Point + Label"))


```


```{r plot by phase bar}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition, phase ,design, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = condition, y = mean, fill = condition)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_grid(design ~ phase, scales = "free_x", space = "free_x" ) +
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("abs", "bar","look", "lookLabel","point", "pointLabel"),
                     labels=c("Control - Later", "Control - Barrier","Test - Look", "Test - Look + Label", "Test - Point", "Test - Point + Label"))
```


Tests against chance per condition. We have 8 trials per subject, so we can use Bayesian t-tests again.
```{r tests against chance}

## one sample bayesian t-tests
library(BayesFactor)


d %>%
  filter(trial_type == "test") %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 0.5))$bf, onlybf = TRUE) %>%
  select(condition,mean,bf) %>%
  knitr::kable(digits = 3)
 
```

Brm Models. Reference level is the test condition.


```{r model}
## model
library(brms)


# controls

data_inf <- d %>%
  filter(trial_type == "test") %>%
  mutate(control  = as.factor(control))

data_inf$control =  relevel(data_inf$control,"no")

# registered  model
bm <- brm(correct ~ control +
              (1 |id) + (control |agent), 
          data = data_inf, family = bernoulli(),
          control = list(adapt_delta = 0.90),
          iter = 5000)

summary(bm)
```




Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type,control) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

```


Plot for trial 1. Very variable but same qualitative pattern.
```{r plot trial 1}
ms <- d %>%
  filter(trial == "1") %>%
  group_by(control,control, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = control, y = mean, fill = control)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("abs", "bar","no"),
                     labels=c("Control - Later", "Control - Barrier","Test"))
```

Effect of target object location on table. Inner = closer to the agent, outer = further away. 
```{r inner vs outer location}
## performance in training and test
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(targetOnTable,control, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = control, y = mean, fill = control,frame = targetOnTable)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~targetOnTable) +
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) +
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("abs", "bar","no"),
                     labels=c("Control - Later", "Control - Barrier","Test"))

```

Condition by trial overall. Looks pretty random.
```{r plot trials}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, trial, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = control)) +
  geom_line(aes(group= control)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

Conditions by agents.
```{r trials per condition and agent}
# d %>%
#   filter(trial_type == "test") %>%
#   group_by(agent,condition) %>%
#   summarise(n = length(agent), 
#             correct = mean(correct)) %>%
#   knitr::kable(digits = 2)
```

Agent effect. For whatever reason, they seem to think that Elephant, Frog and Monkey are particularly informative.
```{r plot agents}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, agent, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = agent, y = mean, col = control)) +
  geom_line(aes(group= control)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

